---
title: "Kpop Report"
author: "Jason Liu, Dillon Tsien, Simon Wu, Ken Huang"
date: "11/21/2021"
output: html_document
---

```{r setup, include=FALSE}
source("chart1.R")
source("chart2.R")
source("chart3.R")
source("table.R")
source("values.R")
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Introduction
We found K-Pop to be a good topic because it’s a media data landscape that is rife with 
layers of racialization and gender. We thought it would be particularly interesting to 
compare the global data trends of K-Pop, especially being situated in a very Western data 
context at UW. Finally, we all found a racial connection to the topic; living in the 
diaspora of Asian-America, understanding the reach of a very much Asian 
(without American)-based phenomenon in the US produces layers of personal significance 
and self-reflexivity in understanding and re-articulating the “Asian-ness” that we’ve 
been dispossessed of.

We will be using the "K-Pop Hits Through The Years" dataset which contains hit/top
songs in K-Pop from the 90s to the latest year using Apple Music and Spotify. Each
song contains information such as its danceability, energy, loudness, and more.
The dataset was obtained from [here](https://www.kaggle.com/sberj127/kpop-hits-through-the-years?select=KPopHits2000.csv).

# Summary
We wanted to analyze the trend of the popularity of K-Pop throughout the years. One way 
we could model this is through looking at specific variables that contribute to popularity 
(danceability, energy, loudness, speechiness, acousticness). For our summary values, we 
thus found the years where the means of each of these variables across the songs released 
that year were the highest:

- Danceability: `r summary_info$max_danceability`
- Energy: `r summary_info$max_energy`
- Loudness: `r summary_info$max_loudness`
- Speechiness: `r summary_info$max_speechiness`
- Acousticness: `r summary_info$max_acousticness`

# Table
The table displays the overall means of the five variables, grouped by year. We chose these 
specific values because they all have intuitive positive correlations with popularity, and 
seem more fundamental components to the songs over things like key (which is hard to correlate 
numerically), duration, time signature, etc.)
```{r echo = F}
knitr::kable(agg_table)
```

# Chart 1
```{r echo = F}
plot1
```

This is a line chart for the danceability of the top hits from 1990 to 2020. The data is aggregated to the year level
and shows an overall increase to the danceability of top Kpop hits as well as a few dips between 2010 and 2020. The
purpose of the graph is to demonstrate a correlation between danceability and time, which is a good indicator of Kpop
songs and their relative popularity and its change over time. Although there are many other features in the Kpop data
set that can be displayed over time such as energy or loudness, the scale is not the same and the resulting graph may
be misleading. In the graph we can also see that the minimum is around 2005 while the maximum is around 2019. 

# Chart 2
```{r echo = F}
danceability_energy_plot
```

This chart is intended to show the relationship between a songs energy and its danceability (mean value of all the
songs for each year). The purpose of this chart is to understand the relationships between two variables of energy 
and danceability and to notice any dense areas in the scatterplot that would correlate to an optimal level of
danceability and energy. Based on the chart, there is a moderate positive correlation between song energy and
danceability. Moreover, newer released songs tend to have a higher song energy and danceability
value/score than older songs.

# Chart 3
```{r echo = F}
boys_chart
girls_chart
```

These are histograms that show the number of boy and girl groups that debuted in each year. The purpose of this chart
is to show the relative success of the kpop industry through how many groups make their debut. In both boy and
girl groups, there seems to be a trend in which the popularity of kpop is steadily growing as the years go on.
